worldmap

### 2024-03-13 analysis/05_model_metrics.Rmd
Get the country labels for studies where available

```{r}
library(tidyverse)
library(lme4)
library(broom.mixed)
library(lmerTest)
library(emmeans)
library(purrr)
```
#### Read in data, get final dataset for models
Get data and put it in long form 
```{r}
#get data
load(here::here("data/meta.rda"))
load(here::here("data/bt_traitfiltered.rda"))
load(here::here("data/rarefied_metrics.rda"))

meta <- meta %>%
  select(study_id, realm, climate, habitat, protected_area, biome_map)

meta <- bt_traitfiltered %>% 
  select(study_id, rarefyid, taxa) %>% distinct() %>%
  left_join(meta)

@@

usethis::use_data(model_data)
```

>>>>

```{r}
library(tidyverse)
library(lme4)
library(broom.mixed)
library(lmerTest)
library(emmeans)
library(purrr)
```
#### Read in data, get final dataset for models
Get data and put it in long form 
```{r}
#get data
load(here::here("data/meta.rda"))
load(here::here("data/bt_traitfiltered.rda"))
load(here::here("data/rarefied_metrics.rda"))
load(here::here("data/rarefyID_cell_centre.rda"))

source(here::here("R/coords2continent.R"))

meta_clean <- meta %>%
  select(study_id, realm, climate, general_treat, treatment, treat_comments, treat_date, habitat, protected_area, biome_map)

meta_clean <- bt_traitfiltered %>% 
  select(study_id, rarefyid, taxa) %>% distinct() %>%
  left_join(meta_clean) %>%
  mutate(rarefyid_join = stringr::str_extract(rarefyid, "[^_]*_[^_]*")) %>%
  left_join(rarefyID_cell_centre %>% select(-STUDY_ID), by = c("rarefyid_join" = "rarefyID")) %>%
  mutate(country = coords2continent(tibble(rarefyID_x = .$rarefyID_x, rarefyID_y = .$rarefyID_y))) %>%
  select(-c(rarefyid_join, cell_extent, rarefyID_x, rarefyID_y, rarefyid)) %>%
  distinct()

#remove NA entries if another country was assigned
na_studies <- meta_clean %>% 
  group_by(study_id) %>% 
  filter(n() > 1, is.na(country))

meta_clean <- setdiff(meta_clean, na_studies)

@@

usethis::use_data(model_data)
usethis::use_data(meta_clean)
```

### 2024-03-13 analysis/figures/06_study_change.Rmd
Get the country labels for studies where available

>>>>

Let's look at more specific combinations
```{r}
load(here::here("data/meta_clean.rda"))

change_groups <- wide_table %>% 
  select(study_id, S, Jaccard_base, starts_with("SES")) %>%
  mutate(across(!study_id, ~case_when(
    . > 0 ~ "pos",
    . < 0 ~ "neg",
    .default = "0"
  )))

change_group_count <- change_groups %>%
  select(-study_id) %>%
  group_by(across(everything())) %>%
  count()

no_change <- change_groups %>% 
  mutate(study_id = as.integer(study_id)) %>%
  filter(across(!study_id, ~. == 0)) %>%
  left_join(meta_clean)

redundancy <- change_groups %>% 
  mutate(study_id = as.integer(study_id)) %>%
  filter(S == "neg", SES_FRic == "0", SES_FDiv == "0", SES_FEve == "0") %>%
  left_join(meta_clean)

redundancy_gain <- change_groups %>% 
  mutate(study_id = as.integer(study_id)) %>%
  filter(S == "pos", SES_FRic == "0", SES_FDiv == "0", SES_FEve == "0") %>%
  left_join(meta_clean)

evenness <- change_groups %>% 
  mutate(study_id = as.integer(study_id)) %>%
  filter(across(!study_id & !SES_FEve, ~. == 0)) %>%
  left_join(meta_clean)

increase <- change_groups %>% 
  mutate(study_id = as.integer(study_id)) %>%
  filter(Jaccard_base == "neg", S == "pos", SES_FRic == "pos", SES_FDiv == "0", SES_FEve == "0") %>%
  left_join(meta_clean)
```

### 2024-03-13 analysis/figures/visualization.Rmd
Get the country labels for studies where available

```{r cars}
library(ggmap)
library(ggplot2)
library(dplyr)
library(ggthemes)
library(mapproj)
library(stringr)
library(cowplot)
library(tidyverse)
```

@@

>>>>

```{r cars}
library(ggmap)
library(ggplot2)
library(dplyr)
library(ggthemes)
library(mapproj)
library(stringr)
library(cowplot)
library(tidyverse)
library(sp)
library(rworldmap)
```

@@

# get country for each cell

# The single argument to this function, points, is a data.frame in which:
#   - column 1 contains the longitude in degrees
#   - column 2 contains the latitude in degrees
coords2continent = function(points){  
  countriesSP <- getMap(resolution='low')
  #countriesSP <- getMap(resolution='high') #you could use high res map from rworldxtra if you were concerned about detail

  # converting points to a SpatialPoints object
  # setting CRS directly to that from rworldmap
  pointsSP = SpatialPoints(points, proj4string=CRS(proj4string(countriesSP)))

  # use 'over' to get indices of the Polygons object containing each point 
  indices = over(pointsSP, countriesSP)

  #indices$continent   # returns the continent (6 continent model)
  #indices$REGION   # returns the continent (7 continent model)
  indices$ADMIN  #returns country name
  #indices$ISO3 # returns the ISO3 code 
}

study_data <- study_data %>% 
  mutate(country = coords2continent(study_data %>% select(rarefyID_x, rarefyID_y)))
